Traditional agroforestry systems in Timor-Leste can store large amounts of carbon in both soil and biomass

### 2024-11-29 manuscript.Rmd
use bayesian approach

packages_needed = c(
  "ggplot2",      # version 3.4.4
  "ggrepel",      # version 0.9.4
  "ggspatial",    # version 1.1.9
  "maps",         # version 3.4.2
  "ggpubr",       # version 0.6.0
  "readxl",       # version 1.4.3
  "data.table",   # version 1.14.8
  "knitr",        # version 1.45
  "BIOMASS",      # version 2.1.11
  "terra",        # version 1.7-55
  "car",          # version 3.1-2
  "lmerTest",     # version 3.1-3
  "lme4",         # version 1.1-35.1
  "Matrix",       # version 1.6
  "performance",  # version 0.10.8
  "flextable"     # version 0.9.5
)

@@

@@

@@

Soil organic carbon stocks (in Mg\ C\ ha$^{-1}$) were calculated as follows:

\begin{equation}
SOC_i = \frac{\sum_i Corg_i \cdot (mfine_i \cdot 10^{-6}) \cdot (Splot \cdot \Delta d)}{Vcyl} (\#eq:soc)
\end{equation}

Where $Corg_i$ is the organic carbon content at depth $i$ (either 0-10, 10-20 or 20-30 cm); $mfine_i$ is the mass of the fine fraction of the soil in the sampling cylinder at depth $i$ (in g), converted into Mg with a factor of 10$^{-6}$; $Splot$ is the surface of a 1-ha plot (10$^8$ cm$^2$); $\Delta d$ is the difference in sample depths (= 10 cm) and $Vcyl$ is the volume of the sampling cylinder (250 cm$^3$). This calculation corresponds to the method recommended by @Poeplau2017 (M4), which correctly takes into account the coarse fraction of the soil. At depth $i$ = 10-20 cm, where the carbon content was not measured (see "Soil measurements" section), we used the average of the carbon content values at 0-10 and 20-30 cm.

@@

```{r add-missing-values}
## add intermediate soil carbon in 10-20 cm depth
data_soil[, Corg := `Corg\n`]
data_soil[, muCorg := mean(Corg, na.rm = TRUE), .(N_PLOT)]
data_soil[is.na(Corg), Corg := muCorg]
```

@@

@@

@@

ggarrange(ggarrange(g1, l1), g2, ncol = 1, heights = c(1,2))
ggsave("fig1.pdf")
```

@@

ggplot(dataC_afs_site[variable %in% c("AGC", "BGC", "SOC")], 
       aes(x = afs, y = mean, fill = variable)) +
  geom_bar(position="stack", stat="identity") + 
  facet_wrap(~site, nrow = 1, strip.position = "bottom") +
  scale_fill_manual(values = c("forestgreen", "darkgoldenrod1", "coral4")) +
  theme_classic() +
  theme(strip.placement = "outside") +
  labs(x = "", y = expression("Carbon stocks (Mg C"*" "*ha^{-1}*")"), fill = "Carbon\npool") +
  scale_y_continuous(expand = c(0, 0))
ggsave("fig2.pdf")
```

@@

```{r fig.id = "plot-lmereg", fig.height = 3.5, fig.width = 7, fig.cap = "Scatter plot of aboveground carbon (AGC; x-axis) and soil organic carbon (SOC; y-axis) stocks. SOC stocks were estimated at the topsoil layer (0-10 cm; left panel) and at the total measured depth (0-30 cm; right panel). Each point represents the median C stock value in a sample plot, and the vertical and horizontal error bars are the 95% confidence interval. The colors correspond to the different agroforestry systems (CF: crop and fallow, SP: silvopasture, YA: young agroforest, HG: home garden, FG: forest garden); the different shapes represent the two sites. The dotted lines represent the (non-significant) linear mixed models between log-transformed AGC and SOC stocks. For each linear mixed model, we report the marginal R^2^ (proportion of variance explained by fixed effects only) and the conditional R^2^ (proportion of variance explained by both fixed and random effects). Both x- and y-axes are log-transformed. One plot (AFS: CF, site: Gariuai) with no trees over 30 cm in circumference at breast height (minimum size for measurement) had AGC stocks estimated at 0 Mg C ha^-1^ and was therefore removed from the linear model and the figure."}
dfpred = expand.grid(AGC_mean = exp(seq(min(log(data_reg$AGC_mean), na.rm = TRUE),
                                        max(log(data_reg$AGC_mean), na.rm = TRUE),
                                        length.out = 20)),
                     depth = c("Soil depth: 0-30 cm", "Soil depth: 0-10 cm")) |>
  merge(dfreg[, c("depth", "intercept", "slope")], by = "depth")
setDT(dfpred)
dfpred[, SOC_mean := exp(intercept + slope * log(AGC_mean))]

@@

## figure
ggplot(dataC_fig, aes(color = afs)) +
  geom_point(aes(x = AGC_mean, y = SOC_mean, shape = site), size = 2) +
  geom_text(data = dfreg, aes(label = paste0("R^{2}*' (marg.) = '*", round(R2_marg, 3))),
            x = -Inf, y = Inf, hjust = -0.1, vjust = 1.2, parse = TRUE, color = 1) +
  geom_text(data = dfreg, aes(label = paste0("R^{2}*' (cond.) = '*", round(R2_cond, 3))),
            x = -Inf, y = Inf, hjust = -0.1, vjust = 2.2, parse = TRUE, color = 1) +
  geom_linerange(aes(x = AGC_mean, y = SOC_mean, ymin = SOC_lwr, ymax = SOC_upr)) +
  geom_errorbarh(aes(y = SOC_mean, xmin = AGC_lwr, xmax = AGC_upr)) +
  geom_line(data = dfpred, aes(x = AGC_mean, y = SOC_mean), lty = 2, col = 1) +
  labs(color = "AFS", x = expression("AGC stocks (Mg C"*" "*ha^{-1}*")"), 
       y = expression("SOC stocks (Mg C"*" "*ha^{-1}*")"), shape = "Site") +
  expand_limits(x = 0, y = 0) +
  scale_color_manual(values = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#E6AB02")) +
  scale_x_log10() +
  scale_y_log10() +
  facet_wrap(~depth) +
  theme_classic()
ggsave("fig3.pdf")
```

@@

>>>>

packages_needed = c(
  "ggplot2",      # version 3.4.4
  "ggrepel",      # version 0.9.4
  "ggspatial",    # version 1.1.9
  "maps",         # version 3.4.2
  "ggpubr",       # version 0.6.0
  "rdryad",       # version 1.0.0
  "readxl",       # version 1.4.3
  "data.table",   # version 1.14.8
  "knitr",        # version 1.45
  "BIOMASS",      # version 2.1.11
  "terra",        # version 1.7-55
  "car",          # version 3.1-2
  "lmerTest",     # version 3.1-3
  "lme4",         # version 1.1-35.1
  "Matrix",       # version 1.6
  "performance",  # version 0.10.8
  "flextable"     # version 0.9.5
)

@@

# get carbon content 
GLOWCAD_files = dryad_download("10.5061/dryad.18931zcxk")
GLOWCAD = read.csv(GLOWCAD_files[[1]][3]) |> 
  subset(grepl("tree", growth.form)) |> 
  subset(tissue %in% c("stem", "root", "coarseroot")) |> 
  subset(biome == "tropical") 
data_ccontent <-

@@

# carbon content

@@

SOC stocks (in Mg\ C\ ha$^{-1}$) in plot $p$ were calculated as follows:

\begin{equation}
SOC_p = \frac{\sum_i Corg_i \cdot (mfine_i \cdot 10^{-6}) \cdot (Splot \cdot \Delta d)}{Vcyl} (\#eq:soc)
\end{equation}

$$SOC_p = \frac{\sum_i Corg_i \cdot (mfine_i \cdot 10^{-6}) \cdot (Splot \cdot \Delta d)}{Vcyl}$$

Where $Corg_i$ is the SOC content at depth $i$ (either 0-10, 10-20 or 20-30 cm); $mfine_i$ is the mass of the fine fraction of the soil in the sampling cylinder at depth $i$ (in g), converted into Mg with a factor of 10$^{-6}$; $Splot$ is the surface of a 1-ha plot (10$^8$ cm$^2$); $\Delta d$ is the difference in sample depths (= 10 cm) and $Vcyl$ is the volume of the sampling cylinder (250 cm$^3$). This calculation corresponds to the method recommended by @Poeplau2017 (M4), which correctly takes into account the coarse fraction of the soil. At depth $i$ = 10-20 cm, where SOC content was not measured (see "Soil measurements" section), we estimated SOC content as a function of SOC content at 0-10 cm and 20-30 cm, assuming a negative exponential model of SOC content decrease with soil depth [@Mishra2009;@Murphy2019]:

\begin{equation}
Corg_{10,20} = Corg_{0,10} \cdot \sqrt{\frac{Corg_{20,30}}{Corg_{0,10}}} (\#eq:intersoc)
\end{equation}

where $Corg_{a,b}$ is the average SOC content between depths a and b (see rationale for equation \@ref(eq:intersoc) in Supplementary Information xx).

@@

```{r add-missing-values}
data_soil[, Corg := `Corg\n`]
## add intermediate soil carbon in 10-20 cm depth under the assumption of an
# organic carbon content that decreases as a negative exponential of depth, we can deduce the carbon content at 10-20 cm with the following function: SOC[10-20] = SOC[0-10]*sqrt(SOC[20-30]/SOC[0-10])
data_soil = merge(
  data_soil, 
  data_soil[, .(
    Corg1020 = Corg[SAMPLE_DEPTH=="0-10"]*
      sqrt(Corg[SAMPLE_DEPTH=="20-30"]/Corg[SAMPLE_DEPTH=="0-10"])), 
    .(N_PLOT)])

data_soil[SAMPLE_DEPTH=="10-20", Corg := Corg1020]
```

@@

```{r add-other-soil-properties}
data_soil_summ <- data_soil |> 
  subset(!is.na(TC)) |> 
  melt(id.vars = c("N_PLOT", "SAMPLE_DEPTH"), 
       measure.vars= c("CLAY", "FINE SILT", "pH\n", "Ca", "CEC\n"))  |> 
  setDT()
data_soil_summ[, variable := gsub("\n", "", variable)]
data_soil_summ <- 
  data_soil_summ[, .(value = mean(as.numeric(value), na.rm = TRUE)), .(N_PLOT, variable)] |> 
  dcast(N_PLOT ~ variable)
data_soil_summ[, fine_soil := CLAY + `FINE SILT`] 
data_sim <- merge(data_sim, data_soil_summ)  
```

@@

```{r}
stan_model <- "
data {
  int<lower=0> N;
  int<lower=1> AF;
  int<lower=1> S;
  int<lower=1,upper=AF> afs[N];
  int<lower=1,upper=S> site[N];
  real clay_sc[N];
  real agc_sc[N];
  real<lower=0> agc[N];
  real<lower=0> soc[N];
  real<lower=0> soc10[N];
}

parameters {
  real mu_a;
  real delta_afs_a[AF];
  real delta_site_a[S];
  real<lower=0> sigma_a;

  real mu_s;
  real delta_afs_s[AF];
  real delta_site_s[S];
  real theta_agc_s;
  real theta_clay_s;
  real<lower=0> sigma_s;

  real mu_s10;
  real delta_afs_s10[AF];
  real delta_site_s10[S];
  real theta_agc_s10;
  real theta_clay_s10;
  real<lower=0> sigma_s10;

  real<lower=0> sigma_site_a;
  real<lower=0> sigma_afs_a;
  real<lower=0> sigma_site_s;
  real<lower=0> sigma_afs_s;
  real<lower=0> sigma_site_s10;
  real<lower=0> sigma_afs_s10;

}

model {
  real pred_a[N];
  real pred_s[N];
  real pred_s10[N];

  for (i in 1:N) {
    pred_a[i] = mu_a + delta_afs_a[afs[i]] + delta_site_a[site[i]];
    pred_s[i] = mu_s + theta_agc_s*agc_sc[i] + theta_clay_s*clay_sc[i] + delta_afs_s[afs[i]] + delta_site_s[site[i]];
    pred_s10[i] = mu_s10 + theta_agc_s10*agc_sc[i] + theta_clay_s10*clay_sc[i] + delta_afs_s10[afs[i]] + delta_site_s10[site[i]];
  }

  agc ~ normal(pred_a, sigma_a);
  soc ~ normal(pred_s, sigma_s);
  soc10 ~ normal(pred_s10, sigma_s);

  // random effects
  delta_afs_a ~ normal(0, sigma_afs_a);
  delta_afs_s ~ normal(0, sigma_afs_s);
  delta_afs_s10 ~ normal(0, sigma_afs_s10);
  delta_site_s ~ normal(0, sigma_site_s);
  delta_site_s10 ~ normal(0, sigma_site_s10);
  delta_site_a ~ normal(0, sigma_site_a);

  //  priors
  theta_agc_s ~ normal(0,1);
  theta_agc_s10 ~ normal(0,1);
  theta_clay_s ~ normal(0,1);
  theta_clay_s10 ~ normal(0,1);
  sigma_a ~ normal(0,1);
  sigma_s ~ normal(0,1);
  sigma_s10 ~ normal(0,1);
  sigma_site_a ~ normal(0,1);
  sigma_afs_a ~ normal(0,1);
  sigma_site_s ~ normal(0,1);
  sigma_afs_s ~ normal(0,1);
  sigma_site_s10 ~ normal(0,1);
  sigma_afs_s10 ~ normal(0,1);
}

"
```

```{r stan}
if (!dir.exists("outputs")) dir.create("outputs")

if (!file.exists("outputs/data_par.csv")) {
  library(parallel)

  cl <- makeCluster(detectCores()-1)
  clusterEvalQ(cl, {library(rstan); library(data.table)})
  clusterExport(cl, "data_sim"); clusterEvalQ(cl, data_sim)
  clusterExport(cl, "stan_model"); clusterEvalQ(cl, stan_model)

  data_par <- parLapply(cl, unique(data_sim$iter), function(i) {
    rstan_options(auto_write = TRUE)

    data_stan <- data_sim |> 
      subset(iter==i) |> 
      dcast(N_PLOT + site + ID_AF + fine_soil ~ variable) |> 
      with(
        list(
          N = length(N_PLOT),
          AF = length(unique(ID_AF)),
          S = length(unique(site)),
          afs = as.numeric(as.factor(ID_AF)), 
          site = as.numeric(as.factor(site)), 
          clay_sc = (fine_soil-mean(fine_soil))/sd(fine_soil),
          agc_sc = (AGC-mean(AGC))/sd(AGC),
          agc = AGC,
          soc = SOC,
          soc10 = SOC10
        ))

    fit <- stan(model_code = stan_model, data = data_stan, 
                iter = 60, warmup = 50, chains = 1)
    pars <- extract(fit) |> 
      lapply(function(x) {
        df <- data.table(iter_stan = 1:dim(x)[1], x) |> 
          melt(id.vars = "iter_stan", variable.name = "level_num")  
        return(df)
      }) |> 
      rbindlist(idcol = "param")
    return(pars)
  }) |> rbindlist(idcol = "iter")

  write.csv(data_par, file = "outputs/data_par.csv", row.names = FALSE)

  stopCluster(cl)

} else data_par <- read.csv("outputs/data_par.csv") |> setDT()

data_par[, effect := tstrsplit(param, "_")[[2]]]
data_par[! effect %in% c("afs", "site", "agc", "clay"), effect := NA]
data_par[, stock := tstrsplit(param, "_")[[3]]]
data_par[is.na(stock) & param != "lp__", stock := tstrsplit(param, "_")[[2]]]
data_par[stock == "a", stock := "agc"]
data_par[stock == "s", stock := "soc"]
data_par[stock == "s10", stock := "soc10"]
data_par[, param := tstrsplit(param, "_")[[1]]]

data_par[, level_num := as.numeric(gsub("V", "", level_num))]
data_par[effect == "afs" & !is.na(level_num), 
         level := levels(as.factor(data_sim$ID_AF))[level_num]]
data_par[effect == "site" & !is.na(level_num),
         level := levels(as.factor(data_sim$site))[level_num]]

df_mu_delta <- 
  data_par[param == "delta" & !is.na(effect)] |> 
  dcast(iter + iter_stan + stock + effect + level ~ param) |> 
  merge(dcast(data_par[param == "mu"], iter + iter_stan + stock ~ param))
df_mu_delta[, `:=`(value = mu + delta, param = "pred_med")]
data_par <- rbind(
  data_par[, c("param", "iter", "iter_stan", "stock", "effect", "level", "value")], 
  df_mu_delta[, c("param", "iter", "iter_stan",  "stock", "effect", "level", "value")]
)

itermaxlp = data_par[param == "lp", iter[which.max(value)]]
pars_summary <- data_par[, .(
  mean = mean(value), 
  maxlp = value[iter==itermaxlp],
  low95 = quantile(value, 0.025), 
  low80 = quantile(value, 0.1), 
  med = median(value), 
  upp80 = quantile(value, 0.9),
  upp95 = quantile(value, 0.975)
), .(
  param, stock, effect, level
)]
```

@@

ggarrange(ggarrange(g1, l1), g2, ncol = 1, heights = c(1,2))
```

@@

ggplot(dataC_afs_site[variable %in% c("AGC", "BGC", "SOC")], 
       aes(x = afs, y = mean, fill = variable)) +
  geom_bar(position="stack", stat="identity") + 
  facet_wrap(~site, nrow = 1, strip.position = "bottom") +
  scale_fill_manual(values = c("forestgreen", "darkgoldenrod1", "coral4")) +
  theme_classic() +
  theme(strip.placement = "outside") +
  labs(x = "", y = expression("Carbon stocks (Mg C"*" "*ha^{-1}*")"), fill = "Carbon\npool") +
  scale_y_continuous(expand = c(0, 0))
```

@@

```{r fig.id = "effect-afs-site", fig.width = 7, fig.height = 3}
labels_stock = function(x) paste(toupper(x), "(Mg/ha)")
labels_effect = function(x) ifelse(x %in% c("afs", "agc"), toupper(x), x)

pars_summary |> 
  subset(param == "pred_med" & stock != "soc10") |> 
  ggplot(aes(y = level)) + 
  geom_segment(aes(x = low95, xend = upp95)) + 
  geom_segment(aes(x = low80, xend = upp80), col = 2, lwd = 3) + 
  geom_point(aes(x = mean), size = 2) +
  facet_grid(
    effect ~ stock, scales = "free", 
    labeller = labeller(stock = labels_stock, effect = labels_effect)) +
  labs(x=NULL, y = NULL) +
  theme_bw()
```

```{r fig.id = "effect-agc-clay", fig.width = 7, fig.height = 2}
labels_effect = function(x) ifelse(x=="agc", "AGC", "clay + fine silt")
pars_summary |> 
  subset(param == "theta")  |> 
  ggplot(aes(y = ifelse(stock=="soc10", "0-10 cm", "0-30 cm"))) + 
  geom_vline(xintercept = 0, lty = 2) +
  geom_segment(aes(x = low95, xend = upp95)) + 
  geom_segment(aes(x = low80, xend = upp80), col = 2, lwd = 3) + 
  geom_point(aes(x = mean), size = 2) +
  facet_wrap(~effect, labeller = labeller(effect = labels_effect)) + 
  labs(x="Effect on SOC", y = NULL) +
  theme_bw()
```

```{r fig.id = "plot-lmereg", fig.height = 3.5, fig.width = 7, fig.cap = "Scatter plot of aboveground carbon (AGC; x-axis) and soil organic carbon (SOC; y-axis) stocks. SOC stocks were estimated at the topsoil layer (0-10 cm; left panel) and at the total measured depth (0-30 cm; right panel). Each point represents the median C stock value in a sample plot, and the vertical and horizontal error bars are the 95% confidence interval. The colors correspond to the different agroforestry systems (CF: crop and fallow, SP: silvopasture, YA: young agroforest, HG: home garden, FG: forest garden); the different shapes represent the two sites. The dotted lines represent the (non-significant) linear mixed models between log-transformed AGC and SOC stocks. For each linear mixed model, we report the marginal R^2^ (proportion of variance explained by fixed effects only) and the conditional R^2^ (proportion of variance explained by both fixed and random effects). Both x- and y-axes are log-transformed. One plot (AFS: CF, site: Gariuai) with no trees over 30 cm in circumference at breast height (minimum size for measurement) had AGC stocks estimated at 0 Mg C ha^-1^ and was therefore removed from the linear model and the figure."}

dfpred <- expand.grid(agc = seq(0, 170, length.out = 20), 
  iter = unique(data_par$iter), 
  iter_stan = unique(data_par$iter_stan)
) |> 
  merge(
    data_par[grepl("soc", stock) & (param =="mu" | effect == "agc")] |> 
      dcast(iter + iter_stan + stock ~ param)
  ) |> 
  merge(
    data_sim[variable=="AGC", .(mua = mean(value), sda = sd(value)), 
             .(iter = as.numeric(as.factor(iter)))]
  ) |> setDT()
dfpred[, pred := (mu - mua*theta/sda) + (theta/sda) * agc]
dfpred <- dfpred[, .(
  mean = mean(pred), 
  lower = quantile(pred, 0.025), 
  upper = quantile(pred, 0.975)
  ), .(agc, stock)]
dfpred[, depth := ifelse(grepl(10, stock), "Soil depth: 0-10 cm", "Soil depth: 0-30 cm")]

@@

## figure
ggplot(dataC_fig, aes(color = afs)) +
  geom_ribbon(data = dfpred, aes(x = agc, ymin = lower, ymax = upper), 
              col = NA, alpha = 0.1) +
  geom_point(aes(x = AGC_mean, y = SOC_mean, shape = site), size = 2) +
  # geom_text(data = dfreg, aes(label = paste0("R^{2}*' (marg.) = '*", round(R2_marg, 3))),
  #           x = -Inf, y = Inf, hjust = -0.1, vjust = 1.2, parse = TRUE, color = 1) +
  # geom_text(data = dfreg, aes(label = paste0("R^{2}*' (cond.) = '*", round(R2_cond, 3))),
  #           x = -Inf, y = Inf, hjust = -0.1, vjust = 2.2, parse = TRUE, color = 1) +
  geom_linerange(aes(x = AGC_mean, y = SOC_mean, ymin = SOC_lwr, ymax = SOC_upr)) +
  geom_errorbarh(aes(y = SOC_mean, xmin = AGC_lwr, xmax = AGC_upr)) +
  geom_line(data = dfpred, aes(x = agc, y = mean), lty = 2, col = 1) +
  labs(color = "AFS", x = expression("AGC stocks (Mg C"*" "*ha^{-1}*")"), 
       y = expression("SOC stocks (Mg C"*" "*ha^{-1}*")"), shape = "Site") +
  expand_limits(x = 0, y = 0) +
  scale_color_manual(values = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#E6AB02")) +
  # scale_x_log10() +
  # scale_y_log10() +
  facet_wrap(~depth) +
  theme_classic()
```

@@

## Supplementary methods

### Calculation of 10-20 cm average carbon content

During field data collection, because the auger length (15 cm) didn't match the target soil sampling depths (10 cm each), we could only accurately sample and analyse the 0-10 cm and 20-30 cm soil depths for SOC content. The SOC content of the intermediate 10-20 cm soil depth had to be estimated based on these first two measurements.

  To reduce the bias in this estimation, we used the standard assumption that SOC content $c(x)$ decreases as an exponential function of soil depth $x$:

  $$c(x) = C_0 \cdot exp(-\lambda\cdot x) $$ 
  where $C_0$ is the carbon content at the surface (depth $x= 0$) and $\lambda$ is the rate at which the carbon content decreases with soil depth. 
  Under this assumption, we can calculate the mean SOC content between depths $x$ and $x+\Delta$ as:

  $$\bar c(x, x+\Delta) = \frac{1}{\Delta}\int_{x}^{x+\Delta}  C_0 \cdot exp(-\lambda\cdot x) dx$$

  $$ \Rightarrow \bar c(x, x+\Delta) = \frac{C_0}{-\lambda \cdot \Delta} \left[ exp(-\lambda\cdot (x+\Delta)) - exp(-\lambda\cdot x) \right]$$

  $$ \Rightarrow \bar c(x, x+\Delta) = \frac{C_0}{\lambda \cdot \Delta} exp(-\lambda\cdot x)\left[1- exp(-\lambda\cdot\Delta) \right]$$
  The average SOC contents between 0-10 cm, 10-20 cm and 20-30 cm can respectively be written as:

  $$C_{0,10} = \frac{C_0}{10\lambda}\left(1- exp(-10\lambda) \right)$$

  $$C_{10,20} = \frac{C_0}{10\lambda} exp(-10\lambda)\left(1- exp(-10\lambda) \right)$$

  $$C_{20,30} = \frac{C_0}{10\lambda} exp(-20\lambda)\left(1- exp(-10\lambda) \right)$$
  We can thus write:

  $$\frac{C_{20,30}}{C_{0,10}} = \frac{\frac{C_0}{10\lambda} exp(-20\lambda)\left(1- exp(-10\lambda) \right)}{\frac{C_0}{10\lambda}\left(1- exp(-10\lambda) \right)} = exp(-20\lambda)$$
  $$ \Rightarrow \lambda = \frac{log(\frac{C_{0,10}}{C_{20,30}})}{20}$$
  We can also write:

  $$ \frac{C_{10,20}}{C_{0,10}} = exp(-10\lambda) $$
  $$\Rightarrow C_{10,20} = C_{0,10} \cdot exp(-10 \cdot \frac{log(\frac{C_{0,10}}{C_{20,30}})}{20})$$

  $$ \Rightarrow C_{10,20} = C_{0,10} \cdot \left( \frac{C_{20,30}}{C_{0,10}}\right)^{\frac{1}{2}}$$
